---
title: "Initial Korean Covid 19"
author: "Larissa Vera"
date: "October 10, 2024"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
require(tidyverse)
require(tigerstats)
require(lubridate)
kRdata <- read.csv(file = 'kRdata.csv')
kRdata <- kRdata %>%
mutate(across(where(is.character), as.factor))

```
### Data is from the Patient_Info dataset from South Korea 1 Jan to 1 May 2020
### This data was retrieved from a downloadable zip file from kaggle

Some of the data was uncoded for sex - sex must be just male or female
77 of the data entries were coded sex  as blank, so we omit these.
state of a patient must be died or alive - we adjust that as well   
  
# Your Question - Is dying independent of sex?

# Methods

Result is categorical 
Sex is Categorical 

The helper file used is cat~cat

$H_0$: Dying is independent of sex.

$H_A$: Dying is dependent of sex.

## Graphical results - use ggplot commands to do this  

```{r}
barchartGC(~result + Sex,data=kRdata)
barchartGC(~result + Sex,data=kRdata, type="percent")

```

The barchart shows the men died at a higher rate compared to women.





  
## Numerical results

```{r}
table1 <- xtabs(~result + Sex, data=kRdata)
rowPerc(table1)
colPerc(table1)
```

The data shown shows among the people who died 64% were men and 36% were women.

## Inferential results 

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

The P value for the chi- square test was 0.001. So the null hypothesis is rejected. Therefore dying is dependent of sex. The fisher exact test shows that men are 2.3 times more likely to die from covid in korea than women in korea. 

## Conclusions

In conclusion the deaths from covid are dependent on sex. In fishers exact test it shows that men are 2.3 times more likely to die from covid than women. The helper file used is cat~cat. The P value in chi- square tes is 0.001 which is less than 0.05 therefore the null hypotheis is rejected.
